---
title: "AAPL, GOOGL, MSFT STOCKS TIME SERIES"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: [ "twitter", "facebook", "menu" ]
    #source_code: embed
    vertical_layout: fill
    navbar:
      - { title: "Storyboard", href: "http://rpubs.com/kleberperez/454744", 
      target: _blank , align: left } 
      - { title: "HealthData.gov", href: "http://rpubs.com/kleberperez/454603", 
      target: _blank , align: left } 
      - { title: "About Kleber Perez", href: "https://www.linkedin.com/in/kleberperez/", 
      target: _blank , align: left }
---

```{r setup, include=FALSE}
library(flexdashboard)
library(quantmod)
library(ggplot2)
library(tidyr)
library(plyr)
library(dygraphs)
library(DT)
library(tidyquant)
library(lubridate)
tickers <- c("AAPL", "GOOGL", "MSFT")
```

```{r,message=FALSE, include=FALSE}
getSymbols(tickers, src = 'yahoo', from = '2014-01-01', to = '2019-01-31')
StockPrices <- do.call(merge, lapply(tickers, function(x) Cl(get(x))))
dateperiod <- c("2014-01-01", "2019-01-31")
```

column 
-----------------------------------------------------------------------

### Stocks Price

```{r}
#dygraph(StockPrices, main = "Stock Prices", group = "Stock") %>%
#    dyAxis("y", label = "USD") %>%
#  dyAxis("x", label = "Time") %>%
#  dyOptions(axisLineWidth = 1.0,  colors = RColorBrewer::brewer.pal(3, "Set2")) %>%
#  dyHighlight(highlightSeriesBackgroundAlpha = 2.0,
#              highlightSeriesOpts = list(strokeWidth = 3)) %>%
#  dyRangeSelector(height = 10)

dygraph(StockPrices) %>%
  dyAxis("y", label = "USD") %>%
  dyOptions(colors = RColorBrewer::brewer.pal(3, "Set2"))
```

### Summary

```{r}
summary(StockPrices)
```   


Row 
-------------------------------------

### Factors
 
```{r fig.width=5, fig.height=5}
what_metrics <- yahooQF(c("Price/Sales", 
                          "P/E Ratio",
                          "Price/EPS Estimate Next Year",
                          "PEG Ratio",
                          "Dividend Yield", 
                          "Market Capitalization"))

metrics <- getQuote(paste(tickers, sep = "", collapse = ";"),what = what_metrics)
metrics <- data.frame(Symbol = tickers, metrics[, 2:length(metrics)])
colnames(metrics) <- c("Symbol", "P-E Ratio", "Price EPS Estimate Next Year", "Div Yield", "Market Cap")
#DT::datatable(metrics)
knitr::kable(metrics)
```

### Closing
 
```{r fig.width = 5, fig.height = 5}
#summary(StockPrices)
knitr::kable(StockPrices)
```


Row 
-----------------------------------------------------------------------

### Important Discoveries / Year

```{r}
# dygraph(StockPrices, group = "Stock") %>%
#   dyAxis("y", label = "Discoveries / Year") %>%
#   dyOptions(colors = RColorBrewer::brewer.pal(3, "Set2")) %>%
#   dyRangeSelector(height = 10)

# getSymbols(tickers, src = 'yahoo', from = '2018-01-01', to = '2019-01-01')
# StockPrices <- do.call(merge, lapply(tickers, function(x) Cl(get(x))))
# dateperiod <- c("2018-01-01", "2019-01-01")

tickers <- c("AAPL", "GOOGL", "MSFT")
cat(getSymbols(tickers), "\n")
closePrices <- do.call(merge, lapply(tickers, function(x) Cl(get(x))))
dateWindow <- c("2018-01-01", "2019-01-31")

dygraph(closePrices, group = "stock") %>%
  dyRebase(value = 100) %>%
  dyRangeSelector(dateWindow = dateWindow)

dygraph(closePrices, main = "Percent", group = "stock") %>%
  dyRebase(percent = TRUE) %>%
  dyRangeSelector(dateWindow = dateWindow)

dygraph(closePrices, main = "None", group = "stock") %>%
  dyRangeSelector(dateWindow = dateWindow)

dygraph(closePrices) %>% 
dyShading(from = "2018-3-1", to = "2018-5-1", color = "#FFE6E6") %>%
  dyShading(from = "2018-8-1", to = "2018-10-1", color = "#CCEBD6")
```

### Factors
 
```{r fig.width=5, fig.height=5}
what_metrics <- yahooQF(c("Price/Sales", 
                          "P/E Ratio",
                          "Price/EPS Estimate Next Year",
                          "PEG Ratio",
                          "Dividend Yield", 
                          "Market Capitalization"))

metrics <- getQuote(paste(tickers, sep = "", collapse = ";"),what = what_metrics)
metrics <- data.frame(Symbol = tickers, metrics[, 2:length(metrics)])
colnames(metrics) <- c("Symbol", "P-E Ratio", "Price EPS Estimate Next Year", "Div Yield", "Market Cap")
#DT::datatable(metrics)
knitr::kable(metrics)
```




Column {.sidebar}
-----------------------------------------------------------------------

> **CONTENT**

***
1. Stock price:
  <br /> Google's stock price steadily rised in the past 5 years. 
  + The Apple and Microsoft have been steady growing trends. 
  + However, Microsoft has the lowest price.
  
2. Key factors:
  + Microsoft has the largest market cap while Apple has the smaller market cap.
  + Apple has the lowest EPS estimated next year.
  + Microsoft has the highest PE ratio while Apple has the lowest PE ratio.

3. Stock volume:
  + Microsoft has the lowest trading volume among the stocks.
 
4. From bollinger bands:
  + Apple has a big drop in last December while Microsoft is relative stable recently. 
 
In conclusion, Microsoft is the stock to choose. 
  + It has the highest stock return.
  + It has a steady trading volume.